Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-23 paper.qmd
Resized Figure 11

five_gau_proj_umap_model1 <- projected_df |>
  filter(type == "data") |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
      geom_point(
        alpha = 0.3) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  xlim(c(-0.18, 0.1)) +
  ylim(c(-0.12, 0.12)) +
  interior_annotation("b", 
                      position = c(0.08, 0.9),
                      cex = 3)

@@

five_gau_proj_umap_model2 <- projected_df |>
  filter(type == "data") |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
      geom_point(
        alpha = 0.3) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  xlim(c(-0.16, 0.1)) +
  ylim(c(-0.1, 0.1)) +
  interior_annotation("b", 
                      position = c(0.08, 0.9),
                      cex = 3)

@@

```{r}
#| label: fig-five-gau-projs
#| fig-cap: "(a) tSNE, (b) UMAP, and (c) PaCMAP"

# fig-height: 6 
# fig-width: 18

>>>>

five_gau_proj_umap_model1 <- projected_df |>
  filter(type == "data") |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
      geom_point(
        alpha = 0.3) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  xlim(c(-0.18, 0.1)) +
  ylim(c(-0.12, 0.12)) +
  interior_annotation("c", 
                      position = c(0.08, 0.9),
                      cex = 3)

@@

five_gau_proj_umap_model2 <- projected_df |>
  filter(type == "data") |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
      geom_point(
        alpha = 0.3) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  xlim(c(-0.16, 0.1)) +
  ylim(c(-0.1, 0.1)) +
  interior_annotation("d", 
                      position = c(0.08, 0.9),
                      cex = 3)

@@

```{r}
#| label: fig-five-gau-projs
#| fig-height: 12
#| fig-width: 8
#| fig-cap: "(a) tSNE, (b) UMAP, and (c) PaCMAP"
